Selective electroporation of the viral envelope

### 2021-04-20 documents/pure_electroporation.tex
Using LLNL-ANSI lpopt
Switched from spral to HSL now that I got the email

The time-domain response can be obtained by the convolution integral with the step or impulse response function, or by manually integrating the differential equation via some integrator.

@@

The fourier transform of both the impulse response and the step response exist, are analytic and of manageable size.

@@

For PSOPT, a further modification was needed, as the library does not support the derivative of the control during .

@@

because the problem depends on the second derivative of sub-nanosecond curves, the scaling varies by about 30 orders of magnitude.
PSOPT [] with IPOPT\cite{implementation2006} solver.

>>>>

The time-domain response can be obtained from the step or impulse response function by evaluating the convolution integral, or by manually integrating the differential equation via some integrator.

@@

The fourier transform of both the impulse response and the step response exist, are analytic and of manageable size; however, the integral of the cost function is extremely unweildy.

\subsection{Optimal control solvers}

An excellent overview of solutions http://plato.asu.edu/sub/nlounres.html

@@

For PSOPT, a further modification was needed, as the library does not support the derivative of the control.

@@

because the problem depends on the second derivative of sub-nanosecond curves, the scaling varies by about 30 orders of magnitude.
PSOPT [] with IPOPT\cite{implementation2006} solver. PSOPT has the advantage of semi-automatic scaling based on bounds.

Both PSOPT and GEKKO's APMonitor backend use the famous ipopt solver. A number of linear solvers can be used. LANL's Tasseff's integration with the SPRAL solver, reportedly faster on large problems, was

It was found very useful to test the

A hard-to-detect lack of convergence would often produce a fallacious simulated output from PSOPT. To double-check that the solution was actually valid, the output was fed through the convolution integral method.

Considerable difficulty was encountered.

\subsection{Optimal control solvers}
